Highly resolved spatiotemporal simulations for exploring mixed fishery dynamics

### 2020-01-26 write_up/parameter_tables.tex
Addressing reviewer comments
Incorparting Coilin and Jean-Marc's comments

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population and recruitment
		dynamics sub-modules.}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Instantaneous rate of fishing mortality in cell $c$
		on day $d$ & - \\
		$M_{c,d}$ & Instantaneous rate of natural mortality in cell $c$
		on day $d$ & - \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the recruitment in cell $c$ for day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & biomass in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate (Beverton Holt)
		or maximum productivity per spawner (Ricker) & kg  \\
		$\beta$ & the stock size required to produce half the maximum rate
		of recruitment (Beverton Holt) or density dependent reduction
		in productivity per capita of SSB & kg \\
		\bottomrule
		\end{tabular}
\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module.}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell $c$ in week $wk$ & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population $p$ & $^\circ$C \\
		$\sigma_{p}$ & Standard deviation of thermal tolerance for
		population $p$ & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & Decay rate for population movement & - \\
		$Hab_{c,p}$ & Habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
		for population $p$ & - \\
		$d_{I,J}$ & Euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module.}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro
		\hspace{0.1cm} kg$^{-1}$ \\
		Le & Step length for vessel & - \\
		$Br$ & Bearing & degrees \\
		$k$ & Concentration parameter for von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}

>>>>

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population and recruitment
		dynamics sub-modules.}
	\label{tab: pop_variable}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{c}{\textbf{Population dynamics}}  \\
		\hhline{===}
		\multicolumn{3}{l}{\textit{Delay-difference model}} \\
		\hline
		$B_{c,d}$ & Biomass in cell $c$ and day $d$ & kg \\
		$Z_{c,d}$ & Total mortality in cell $c$ for day $d$ & - \\
		$R_{c, \tilde{y}}$  &Annualy recruited fish in cell &  yr\textsuperscript{-1} \\
		$\rho$ & Brody's growth coefficient & yr\textsuperscript{-1} \\
		$Wt_{R}$ & Weight of a fully recruited fish & kg \\
		$Wt_{R-1}$ & Weight of a pre-recruit fish & kg \\
		$\alpha_{d}$ & Proportion of annually recruited fish recruited
		during day $d$ & - \\
		\hline
		\multicolumn{3}{l}{\textit{Baranov catch equation}} \\
		\hline
		$C_{c,d}$ & Catch from cell $c$ for day $d$ & kg \\
		$F_{c,d}$ & Rate of fishing mortality in cell $c$
		on day $d$ & $d^{-1}$ \\
		$M_{c,d}$ & Rate of natural mortality in cell $c$
		on day $d$ & $d^{-1}$ \\
		$B_{c,d}$ & Biomass in cell $c$ on day $d$ & kg \\
		\hline
		\multicolumn{3}{c}{\textbf{Recruitment dynamics}} \\
		\hhline{===}
		$\tilde{R}_{c,d}$ & is the number of fish recruited in cell $c$ for day $d$ & $d^{-1}$ \\
		$\alpha$ & the maximum recruitment rate (Beverton Holt)
		or maximum productivity per spawner (Ricker) & number fish  \\
		$\beta$ & the stock size required to produce half the maximum rate
		of recruitment (Beverton Holt) or density dependent reduction
		in productivity per capita of SSB & number fish \\
		\bottomrule
		\end{tabular}
\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for population movement sub-module.}
	\label{tab:pop_move}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		\multicolumn{3}{l}{\textit{Thermal tolerance}} \\
		\hline
		$T_{c,wk}$ & Temperature for cell $c$ in week $wk$ & $^\circ$C \\
		$\mu_{p}$ & Mean of the thermal tolerance for population $p$ & $^\circ$C \\
		$\sigma_{p}$ & Standard deviation of thermal tolerance for
		population $p$ & $^\circ$C \\
		\hline
		\multicolumn{3}{l}{\textit{Population movement model}} \\
		\hline
		$\lambda$ & Decay rate for population movement & - \\
		$Hab_{c,p}$ & Habitat suitability for cell $c$ and
		population $p$ & - \\
		$Tol_{c,wk,p}$ & Thermal tolerance for in cell $c$ at week $wk$
		for population $p$ & - \\
		$d_{I,J}$ & Euclidean distance between cell $I$ and cell $J$ & - \\
		\bottomrule
		\end{tabular}
	\end{table}

\begin{table}[!ht]
	\centering
	\caption{Description of variables for fleet dynamics sub-module.}
	\label{tab:fleet_dyn}
	\begin{tabular}{p{1.5cm} p{8cm} p{1.5cm}}
		\toprule
		Variable & Meaning & Units \\
		\hline
		$Rev$ & Revenue from fishing tow & \euro \\
		$L_{p}$ & Landings of population $p$ & kg \\
		$Pr_{p}$ & Average price of population $p$ & \euro.kg$^{-1}$ \\
		Le & Step length for vessel & - \\
		$Br$ & Bearing & degrees \\
		$k$ & Concentration parameter for von mises distribution & - \\
		$\beta_{1}$ & shape parameter for step function & - \\
		$\beta_{2}$ & shape parameter for step function & - \\
		$\beta_{3}$ & shape parameter for step function & - \\
		\bottomrule
	\end{tabular}
\end{table}
